Discrete Quantum Theories and Computing

### 2019-04-29 dissertation.tex
dissertation.lyx Acknowledgments and "6.1 Summary" Fix small things...

\item My classmates or friends in NTU, including Hao-Chun Lee (李浩君),
Hsien-Ching Kao (高憲慶), Wei Cheng (鄭維), Chin-Yi Lin (林金毅), Chun-Ting
Chen (陳俊廷), and Prof.~Chenying Huang (黃貞穎), \ldots , etc.

@@

The theories over finite fields started with unrestricted discrete
fields (Chapter~\ref{chap:Unrestricted-Finite-Fields}), then advanced
to a more reasonable framework based on complexifiable discrete fields
(Secs.~\ref{discretequantumtheoryI} to~\ref{discretequantumcomputingI}),
but both of them lack a notion of probability and support unnaturally
efficient deterministic quantum algorithms. A still more plausible
discrete theory with cardinal probabilities was proposed (Secs.~\ref{sec:Discrete-Quantum-Theory-(II)}
and~\ref{discretequantumcomputingII}), where conventional quantum
theory and computing emerge in a local sense, but lacking arithmetic
operations among cardinal probabilities still posed difficulty to
define expectation values. Since the axiomatic approach looked unlikely
to provide sensible real-valued probability measures over finite fields
(Sec.~\ref{sec:Toward-IVPM}), we shifted our attention to directly
embed our limitation of distinguishability into the theory to define
QIVPM.

>>>>

\item My classmates or friends in NTU, including Hao-Chun Lee (李浩君),
Hsien-Ching Kao (高憲慶), Wei Cheng (鄭維), Chin-Yi Lin (林金毅), Chun-Ting
Chen (陳俊廷), and Prof.~Chen-Ying Huang (黃貞穎), \ldots , etc.

@@

The theories over finite fields started with unrestricted discrete
fields (Chapter~\ref{chap:Unrestricted-Finite-Fields}) and then
advanced to a more reasonable framework based on complexifiable discrete
fields (Secs.~\ref{discretequantumtheoryI} to~\ref{discretequantumcomputingI}),
but both of them lack a notion of probability and support unnaturally
efficient deterministic quantum algorithms. A still more plausible
discrete theory with cardinal probabilities was proposed (Secs.~\ref{sec:Discrete-Quantum-Theory-(II)}
and~\ref{discretequantumcomputingII}), where conventional quantum
theory and computing emerge in a local sense, but lacking arithmetic
operations among cardinal probabilities still posed difficulty to
define expectation values. Since the axiomatic approach looked unlikely
to provide sensible real-valued probability measures over finite fields
(Sec.~\ref{sec:Toward-IVPM}), we shifted our attention to directly
embed our limitation of distinguishability into the theory to define
QIVPM.
